---
title: "Developing Data Products - Week 4 Assignment"
author: "sckamath"
date: "19 July 2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

## Coursera Reproducible Pitch

This project is for Coursera Data Science course - Developing Data Products: week 4. As part of this, a shiny app is developed and deployed it on the shiny server. The link is https://sckamath.shinyapps.io/rshiny/. The code can be found at https://github.com/sckamath/shinyapps 

## Overview

The shiny app plots graph against miles per gallon (mpg) for different variables from the mtcars dataset.  The objective of this application is to assist users in selecting cars based on these variables and their requirements.

The data set is as follows:

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(car)
head(mtcars)
```

## Analysis

Here we can see the relationship between three variables: miles per gallon (mpg), cylinder (cyl), transmission and gears.

```{r echo=FALSE,warning=FALSE, message=FALSE}

scatterplotMatrix(~mpg+cyl+am+gear, data=mtcars, cex.axis=1.5)
```

## UI Code

```{r, echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)

shinyUI(fluidPage(
  
  # Application title
  titlePanel("Cars Dataset - Miles per Gallon"),
  
  sidebarPanel(
    
    radioButtons("variable", "Variable:", 
                c("Cylinders" = "cyl",
                  "Transmission" = "am",
                  "Gears" = "gear"))
  ),
  
  mainPanel(
    # Output: Formatted text for caption ----
    h3(textOutput("caption")),
    
    # Output: Plot of the requested variable against mpg ----
    plotOutput("mpgPlot")
  )
))
```

## Server Code

```{r, echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
library(plotly)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("mpg vs ", input$variable)
  })
  
  output$caption <- renderText({
    formulaText()
  })

  output$mpgPlot <- renderPlot({
    ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
})
```

