---
title: "Developing Data Products - Week 4 Assignment"
author: "Chandrakanth Kamath"
date: "19 July 2020"
runtime: shiny
output: html_document

---

## Coursera Reproducible Pitch

This project is for Coursera Data Science course - Developing Data Products: week 4. As part of this, a shiny app is deployed at https://sckamath.shinyapps.io/Cars/ on the shiny server. The code can be found at https://github.com/sckamath/shinyapps 

## Overview

This is an interactive version of the Shiny app with live documentation that helps user to navigate through the app. I have used the same UI and Server code.  This app plots graphs against miles per gallon (mpg) for different variables from the mtcars dataset.

The dataset is as follows:

```{r}
head(mtcars)
```

Please select the variables such as Cylinders, Transmission and Gears.  Based on these selections the app will generate the miles per gallon as per the selection variables.

```{r, echo=FALSE}
library(shiny)
library(ggplot2)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

  # Application title
  # titlePanel("Cars Dataset - Miles per Gallon"),
  
  inputPanel(
    
    radioButtons("variable", "Variable:", 
                c("Cylinders" = "cyl",
                  "Transmission" = "am",
                  "Gears" = "gear"))
  )
```


This is the graph which indicates the miles per gallon (mpg).  Example: if you select "gears", there are few cars that offer higher mpg with gears >= 5.  You may select various other variables to assess the mpg.


```{r, echo=FALSE}
  renderPlot({
    ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
```

